Bird beak's elaboration and innovation

### 2022-02-23 Analysis/10-Figure1.Rmd
renamed figure1

# pdf(file = "Figure_1a.pdf", height = 11, width = 5.5)
# ## Plot the phylo ellipse
# grey_palette <- c(colour.palette(8), "grey")
# par(mfrow = c(2,1), bty = "n")
# plot.one.ellipse(superorder_shapespace, ID = c(1,9), colours = grey_palette, x = TRUE, y = TRUE, main = "A")
# legend("topright", lwd = 5, col = grey_palette[c(1,9)], lty = 1, legend = c("Aequornithes' median variance-covariance", "Overall phylogenetic's median variance-covariance"), bg = "white")
# plot.one.proj.rej(results$super_results_between, ID = 1, colours = grey_palette)
```

```{r}
box_size <- 1.5
pdf(file = "../Manuscript/Figures/Figure_1.pdf", height = box_size*8, width = box_size*10)

>>>>

# pdf(file = "Figure1a.pdf", height = 11, width = 5.5)
# ## Plot the phylo ellipse
# grey_palette <- c(colour.palette(8), "grey")
# par(mfrow = c(2,1), bty = "n")
# plot.one.ellipse(superorder_shapespace, ID = c(1,9), colours = grey_palette, x = TRUE, y = TRUE, main = "A")
# legend("topright", lwd = 5, col = grey_palette[c(1,9)], lty = 1, legend = c("Aequornithes' median variance-covariance", "Overall phylogenetic's median variance-covariance"), bg = "white")
# plot.one.proj.rej(results$super_results_between, ID = 1, colours = grey_palette)
```

```{r}
box_size <- 1.5
pdf(file = "../Manuscript/Figures/Figure1.pdf", height = box_size*8, width = box_size*10)
